Weighted Model Counting with Conditional Weights

### 2020-07-29 paper/paper.tex
Writing and editing about BNs and function spaces

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
    0}$ be arbitrary functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$.
  We define the following operations:
  \begin{description}
  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      \overline{A}(\tau) = 1 - A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
    \to \mathbb{R}_{\ge 0}$ such that
    \[
      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (\alpha A)(\tau) = \alpha \cdot A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
    \[
      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
    \]
    for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}

@@

\todo[inline]{Define 'CPT'}

In line with the names of previous encodings, we shall call this encoding
\texttt{db20}. Let $V$ denote the set of random variables in a Bayesian network.
For any random variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of
parents of $X$ and $\im X$ denote the set of possible values. We will use the
Bayesian network in \cref{fig:example_bn} as a running example throughout this
section. For this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
$\im T = \{ l, m, h \}$.

>>>>

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
    0}$ be functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We define
  the following operations:
  \begin{description}
  \item[Addition:] $A+B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is a function
    such that $(A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)$ for all $\tau \in
    2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}\colon 2^X \to \mathbb{R}_{\ge 0}$ is a function
    such that $\overline{A}(\tau) = 1 - A(\tau)$ for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$
    is a function such that $(A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau
    \cap Y)$ for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A\colon 2^X \to \mathbb{R}_{\ge 0}$ is a
    function such that $(\alpha A)(\tau) = \alpha \cdot A(\tau)$ for all $\tau
    \in 2^X$.
  \item[Projection:] $\exists_xA\colon 2^{X \setminus \{ x \}} \to
    \mathbb{R}_{\ge 0}$ is a function such that $(\exists_xA)(\tau) = A(\tau) +
    A(\tau \cup \{ x \})$ for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}

@@

\todo[inline]{In line with the names of previous encodings, we shall call this
  encoding \texttt{db20}.}

A \emph{Bayesian network} is a directed acyclic graph with random variables as
vertices that defines a probability distribution over them. Let $V$ denote the
set of random variables and $X \in V$ be a random variable. Let $\im X$ denote
the set of possible values of $X$ and $\mathrm{pa}(X)$ denote the set of its
parents. The full probability distribution is then equal to
\begin{equation} \label{eq:factorisation}
  \prod_{X \in V} \Pr(X \mid \mathrm{pa}(X)).
\end{equation}
If all random variables are discrete (and we only consider discrete Bayesian
networks in this paper), the probabilities contained in each factor of
\cref{eq:factorisation} can be summarised in a table known as a
\emph{conditional probability table} (CPT). See \cref{fig:example_bn} for an
example Bayesian network which we will refer to throughout this section. For
this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F)
= \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m,
h \}$.
